For submission to the Journal of Integrated Pest Management

### 2021-03-30 ofv_fife_2021.Rmd
changed name of image folder to 'figure' for easy copypasta into dissertation

### Figures
```{r, fig_1, warning=FALSE}
grid::grid.raster(tiff::readTIFF("images/symp-ofv-lir.tif"))
```

```{r, fig_2, warning=FALSE}
grid::grid.raster(tiff::readTIFF("images/symp-ofv-asp.tif"))
```

```{r, fig_3, warning=FALSE}
grid::grid.raster(tiff::readTIFF("images/b_cali.tif"))
```

```{r, fig_4, warning=FALSE}
grid::grid.raster(tiff::readTIFF("images/other_mites.tif"))
```

<!-- ```{r, fig_4, warning=FALSE} -->
<!-- grid::grid.raster(tiff::readTIFF("images/fungus_mite.tif")) -->
<!-- ``` -->

>>>>

### Figures
```{r, fig_1, warning=FALSE}
grid::grid.raster(tiff::readTIFF("figure/symp-ofv-lir.tif"))
```

```{r, fig_2, warning=FALSE}
grid::grid.raster(tiff::readTIFF("figure/symp-ofv-asp.tif"))
```

```{r, fig_3, warning=FALSE}
grid::grid.raster(tiff::readTIFF("figure/b_cali.tif"))
```

```{r, fig_4, warning=FALSE}
grid::grid.raster(tiff::readTIFF("figure/other_mites.tif"))
```

<!-- ```{r, fig_4, warning=FALSE} -->
<!-- grid::grid.raster(tiff::readTIFF("figure/fungus_mite.tif")) -->
<!-- ``` -->
